### 2017-03-01 paper/chapters/vae/cvae.tex
reformatted CVAE

Instead of using VAEs in a completely unsupervised manner on a unlabeled dataset, it is also possible to learn from datasets where a small subset of datapoints has corresponding labels while most datapoints are still unlabeled.
Techniques learning from such datasets are called semi-supervised learning and can improve performance significantly.\\

To adjust the VAE model to the semi-supervised case, we have to add an random variable $y$ corresponding to the corresponding label if available.
Thus we can extend the distributions as shown below.

%The modified setup of the semi-supervised case for the variational autoencoder can be formalized as follows.
%Dataset $X$ of size $N$ with observations $x_i$ with $i<N$ where for some small subset of observations $x_i$ the corresponding labels $y_i$ are known.
%We denote the labelled subset as $~p_l(x,y)$ and the unlabelled dataset as $~p_u(x,y)$.
%\begin{equation}

%\end{equation}
%Instead of randomly generated data, generation of output conditioned on some prior information is needed.
%A few examples would be super-resolution of images (citation!), prediction of subsequent frames of an video or other prediction tasks

%Conditional VAE is a modification of the original VAE framework to support conditioning on another variable $y$ in addition to the input data $x$.

%To support conditional distributions, the following relations have to be rewritten:
\begin{itemize}
\item \textbf{Sampling from data space}: $x \sim p_\theta(x|y,z)$ instead of $x \sim p_\theta(x|z)$.\\
\item \textbf{Probabilistic encoder}: $q_\theta(z|x,y)$ instead of just $q_\theta(z|x)$.\\
\item \textbf{Probabilistic decoder}: $p_\phi(x|y,z)$ instead of just $p_\phi(x|z)$.\\
\end{itemize}

These modifications allows us to formalize the new objective functionas shown in equations \ref{eq:cvae_labels} and \ref{eq:cvae_unknown}.

>>>>

Instead of using VAEs in a completely unsupervised manner on a unlabeled dataset, it is also possible to learn from datasets where a small subset of datapoints has corresponding labels while most datapoints are still unlabeled.
Techniques learning from such datasets are called semi-supervised learning and can improve performance significantly~\cite{cvae:2014}\cite{cvae_2:2015}.\\
%
To adjust the VAE model to the semi-supervised case, we have to add a random variable $y$ corresponding to the label if available.\\\\
First, instead of using samples from the dataset alone we are now also conditioning on $y$, formally 
$x \sim p_\theta(x|y,z)$ instead of $x \sim p_\theta(x|z)$.\\
Then the probabilistic encoder and decoder can be written as $q_\theta(z|x,y)$ and $p_\phi(x|y,z)$ respectively.\\
%
%The modified setup of the semi-supervised case for the variational autoencoder can be formalized as follows.
%Dataset $X$ of size $N$ with observations $x_i$ with $i<N$ where for some small subset of observations $x_i$ the corresponding labels $y_i$ are known.
%We denote the labelled subset as $~p_l(x,y)$ and the unlabelled dataset as $~p_u(x,y)$.
%\begin{equation}
%
%\end{equation}
%Instead of randomly generated data, generation of output conditioned on some prior information is needed.
%A few examples would be super-resolution of images (citation!), prediction of subsequent frames of an video or other prediction tasks
%
%Conditional VAE is a modification of the original VAE framework to support conditioning on another variable $y$ in addition to the input data $x$.
%
%To support conditional distributions, the following relations have to be rewritten:
%
These modifications allows us to reformulate the objective function $\mathcal{L}$ from Equation~\ref{eq:vae_obj} in equations \ref{eq:cvae_labels} and \ref{eq:cvae_unknown}.
